Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-01 Docs/TODAES/paper.tex
minor changes

\hyphenation{ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

The most basic directive of OpenMP is the ``\#pragma omp parallel for'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:

@@

\vspace{3 mm}
In the above example, the for loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\#pragma omp critical'' directive is routinely used.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.3]{figures/vzArch.png} 
	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

\vspace{3 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

@@

It is possible to inform to ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. Those values that change for each test will generate a possible solution and obey the constraints. If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (i.e., $A.x \leq b$).

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS Approach.}
	\label{ESBMC-Multi-core}
\end{figure}

ESBMC-SS obtains the problem specification represented by a C program. The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores. All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}. Note that there is no shared-memory (or message-passing) mechanism among threads. In particular, different threads are managed by the OpenMP API, which is responsible for the thread life-cycle: start, running, and dead states, using different values as condition. After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment. During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time. If all threads of the batch processing are terminated, then ESBMC-SS finishes its execution.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS Approach. }
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB Approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
	\caption{Binary Step Calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
 GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
     if(chunk.right - chunk.left > largestChunk){
           largestChunk = chunk.right - chunk.left;
           largest = chunk;
     }
   }	
   chunks.remove(largest);	
   int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
      if(largest.right - largest.left > 1)
         chunks.add(new chunk(largest.left, median - 1));	
      if(largest.right != largest.left)
         chunks.add(new chunk(median + 1, largest.right);
    }
   return median;
 }
\end{lstlisting}

>>>>

\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations ({\it i.e.},\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

The most basic directive of OpenMP is the ``\textit{\#pragma omp parallel for}'', which parallelizes the enclosing loop; a basic OpenMP example is shown below:

@@

\vspace{3 mm}
In the above example, the for loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.3]{figures/vzArch.png} 
	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

\vspace{3 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

@@

It is possible to inform to ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. Those values that change for each test will generate a possible solution and obey the constraints. If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

ESBMC-SS obtains the problem specification represented by a ANSI-C program. The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores. All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}. Note that there is no shared-memory (or message-passing) mechanism among threads. In particular, different threads are managed by the OpenMP API, which is responsible for the thread life-cycle: start, running, and dead states, using different values as condition. After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment. During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time. If all threads of the batch processing are terminated, then ESBMC-SS finishes its execution.

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
	\caption{Binary step calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{lstlisting}[caption=Steps calculation using intervals.,label=Steps-Calculation-using-Intervals]
 GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
     if(chunk.right - chunk.left > largestChunk){
           largestChunk = chunk.right - chunk.left;
           largest = chunk;
     }
   }	
   chunks.remove(largest);	
   int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
      if(largest.right - largest.left > 1)
         chunks.add(new chunk(largest.left, median - 1));	
      if(largest.right != largest.left)
         chunks.add(new chunk(median + 1, largest.right);
    }
   return median;
 }
\end{lstlisting}
